ms2

### 2017-08-28 ms2/ms2_display.Rmd
simplified ineq

>>>>

## Unevenness of consumption

For each drug, what fraction of people took that drug? Of people who took it, how many had one claim? How many claims are accounted for by singleton users? This is data from 2011.

```{r ineq_table}
pct = function(x) round(x*100, 2)

ineq %>%
  # use only 2011 data
  filter(year==2011, unit_type=='state') %>%
  # sum across unit types
  group_by(drug_group, n_claims) %>%
  summarize(n_bene=sum(n_bene)) %>%
  ungroup() %>%
  mutate(n_class_claims = n_claims * n_bene) %>%
  group_by(drug_group) %>%
  mutate(pct_bene=pct(n_bene/sum(n_bene)),
         pct_claims=pct(n_class_claims/sum(n_class_claims))) %>%
  select(drug_group, n_claims, pct_bene, pct_claims) %>%
  mutate(n_claims=fct_other(factor(n_claims), keep=0:2, other_level='3+')) %>%
  group_by(drug_group, n_claims) %>%
  summarize_at(vars(pct_bene, pct_claims), sum) %>%
  ungroup() %>%
  gather('key', 'val', pct_bene:pct_claims) %>%
  mutate(key2=str_c(n_claims, ':', key)) %>%
  select(drug_group, key2, val) %>%
  spread(key2, val) %>%
  kable
```
